Simulating a flock of birds

### 2017-12-17 tex/article.tex

To determine the critical noise parameter $\eta_c$ we used a quadratic fit model
to to fit the falling curve for $\eta < \eta_c$ and a linear fit for $\eta > 
\eta_c$, both visible in figure~\ref{fig:va_over_eta}. $\eta_c$ is then set to 
the intersection of the fit curves. Hereby we determine $\eta_c = 4.25$ for $N=400$.

>>>>

To determine the critical noise parameter $\eta_c$ we used a quadratic fit model
to fit the falling curve for $\eta < \eta_c$ and a linear fit for $\eta > 
\eta_c$, both visible in figure~\ref{fig:va_over_eta}. $\eta_c$ is then set to 
the intersection of the fit curves. Hereby we determine $\eta_c = 4.25$ for $N=400$.
